Network Structure, Efficiency, and Performance in WikiProjects

### 2017-08-07 paper.tex
Add references.

Our analysis combines multiple datasets from the English-language Wikipedia.
For information about edit history, we used a publicly-available dataset containing
metadata about all edits between TODO.
To get the rating history of each article,
we wrote a script to scrape the daily logs produced by WPBot1.0 for each WikiProject
between TODO.
Finally, we used a publicly-available log of page events (including rename events)
to reconstruct the unique identifier for each article title mentioned in the rating history logs.

@@

To model the relationship between performance, efficiency, and network structure,
we must have a way to quantify performance and efficiency.
We define these quantities on a per-WikiProject basis to enable comparisons across different
projects.
Our definitions are inpsired by work modeling collective problem-solving as an optimization
problem \cite{}.
The efficiency quantifies how quikly a solution is reached,
while the performance quantifies how good the eventual solution is.

>>>>

Our analysis combines multiple datasets from the English-language Wikipedia.
For information about edit history, we used a publicly-available dataset containing
metadata about all edits between TODO.
To get the rating history of each article,
we wrote a script to scrape the daily logs produced by WP 1.0 Bot for each WikiProject
between TODO.
Finally, we used a publicly-available log of page events (including rename events)
to reconstruct the unique identifier for each article title mentioned in the rating history logs.

@@

To model the relationship between performance, efficiency, and network structure,
we must have a way to quantify performance and efficiency.
We define these quantities on a per-WikiProject basis to enable comparisons across different
projects.
Our definitions are inpsired by work modeling collective problem-solving as an optimization
problem \cite{lazer_network_2007, mason_propagation_2008, mason_collaborative_2012, grim_scientific_2013, barkoczi_social_2016}.
The efficiency quantifies how quikly a solution is reached,
while the performance quantifies how good the eventual solution is.
